CCVPN: Content Centric Virtual Private Networking

### 2016-12-21 paper/main.tex
adding first throughput results to the paper

To investigate the processing overhead we measure the average time demand for computing the interests' encapsulation (in public and symmetric key versions), interest decapsulation, content encryption, and content decryption for different content packet sizes. We also measure the state consumption for these same four functions.

To compute the overall network throughput, we consider four content packet sizes ($4096$, $10 \times 4096$, $10^2 \times 4096$, and $10^3 \times 4096$). For each content packet size, we measure the average data-rate for transmissions of 1 to 100,000 different interests issues per consumer. We also vary the number of consumers and producers from 1 to 10 of each. Finally, in addition to the network throughput, we also exhibit the total transmission delay for each of the experiments.

@@

>>>>

To investigate the processing overhead we measure the average time demand for computing the interests' encapsulation (in public and symmetric key versions), interest decapsulation, content encryption, and content decryption for different content packet sizes (1024, 4096, 16384, and 65536 bytes). We also measure the state consumption for these same four functions.

To compute the overall network throughput we measure the average data-rate for transmissions of 1 to 1,000,000 different interests issues per consumer. We also vary the number of consumers and producers from 1 to 10 of each. Finally, in addition to the network throughput, we also exhibit the total transmission delay for each of the experiments.

@@

\begin{table}[!h]
\centering
\caption{Interest encapsulation processing times}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|}
\hline
Encapsulation mode   & Encapsulation & Decapsulation \\ \hline
Public Key  & 444$\mu s$           & 449$\mu s$           \\ \hline \cline{4-5} 
Symmetric Key & TODO          & TODO          \\ \hline
\end{tabular}
\end{table}

\begin{table}[!h]
\centering
\caption{Content encryption and decryption times for different payload sizes}
\label{my-label}
\begin{tabular}{|l|l|l|}
\hline
Packet size        & Encryption & Decryption \\ \hline
$1024$B & 125$\mu s$        & 193$\mu s$        \\ \hline
$4096$B & 141$\mu s$        & 220$\mu s$        \\ \hline
$16384$B & 220$\mu s$        & 367$\mu s$        \\ \hline
$65536$B & 519$\mu s$        & 702$\mu s$        \\ \hline
\end{tabular}
\end{table}

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{throughput_pk_1x1}
\caption{Throughput in public key mode}
\label{throughput1x1}
\end{figure}
